\documentclass[10pt, letterpaper]{article}

\usepackage[
    ignoreheadfoot,
    top=2.5 cm,
    bottom=2.5 cm,
    left=2.2 cm,
    right=2.2 cm,
    footskip=1.2 cm,
]{geometry}

\usepackage{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0,0,0}

\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Prakhar Bhandari Resume},
    pdfauthor={Prakhar Bhandari},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}

\usepackage{paracol}
\usepackage{changepage}
\usepackage{needspace}

\raggedright
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.2cm}
\pagenumbering{gobble}

\titleformat{\section}
{\needspace{4\baselineskip}\bfseries\large}
{}{0pt}{}
[\vspace{2pt}\titlerule]

\titlespacing{\section}{-1pt}{0.5cm}{0.3cm}

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}

\newenvironment{highlights}{
\begin{itemize}[topsep=0.15cm,parsep=0.15cm,itemsep=0.05cm,leftmargin=12pt]
}{
\end{itemize}
}

\newenvironment{onecolentry}{
\begin{adjustwidth}{0cm}{0cm}
}{
\end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
\onecolentry
\def\secondColumn{#2}
\setcolumnwidth{\fill,4.7cm}
\begin{paracol}{2}
}{
\switchcolumn \raggedleft \secondColumn
\end{paracol}
\endonecolentry
}

\begin{document}

\begin{center}

{\fontsize{26pt}{26pt}\selectfont Prakhar Bhandari}

\vspace{6pt}

Jaipur \,|\, 
\href{mailto:prakharb2k6@gmail.com}{prakharb2k6@gmail.com} \,|\, 
\href{mailto:f20230458@goa.bits-pilani.ac.in}{BITS Email} \,|\, 
9136540772 \,|\, 
\href{https://linkedin.com/in/prakharbhandari13}{LinkedIn} \,|\, 
\href{https://github.com/darelife}{GitHub}

\end{center}

%------------------------------------------------
\section{Education}

\begin{twocolentry}{2023 -- 2027}
\textbf{BITS Pilani, Goa Campus}
\end{twocolentry}

B.E. (Hons.) Computer Science

CGPA: 8.15

Relevant Coursework: Data Structures, Digital Design, OOP, DBMS, OS

\vspace{0.2cm}

\begin{twocolentry}{2021 -- 2023}
\textbf{Apex International School, Jaipur}
\end{twocolentry}

Class XII – 92\%

\vspace{0.2cm}

\begin{twocolentry}{2019 -- 2021}
\textbf{RN Podar School, Mumbai}
\end{twocolentry}

Class X – 93.5\%

%------------------------------------------------
\section{Technical Skills}

\begin{onecolentry}
\textbf{Languages:} C++, Python, C, Java, Golang
\end{onecolentry}

\vspace{0.1cm}

\begin{onecolentry}
\textbf{Web / Backend:} Next.js, React.js, Express.js, Flask, API Development
\end{onecolentry}

\vspace{0.1cm}

\begin{onecolentry}
\textbf{Databases:} PostgreSQL, MongoDB, MySQL, Firebase
\end{onecolentry}

\vspace{0.1cm}

\begin{onecolentry}
\textbf{Tools / Platforms:} Git, Docker, Google Cloud Platform, GitHub Actions, Postman
\end{onecolentry}

%------------------------------------------------
\section{Work Experience}

\begin{twocolentry}{May 2025 -- Jul 2025}
\textbf{SWE Intern, AI Gurukul}
\end{twocolentry}

\begin{highlights}

\item Built AI agents using CrewAI integrated with Gemini API and PostgreSQL.

\item Implemented a PDF-based Retrieval-Augmented Generation pipeline using chunk overlap, BM25 keyword retrieval and vector search.

\item Improved LLM reliability using prompt injection defense and context injection strategies.

\end{highlights}

%------------------------------------------------
\section{Projects}

\begin{twocolentry}{
\href{https://chromewebstore.google.com/detail/codeforces-helper/ahoeafmlmoohkkalcickdnkifpfnolpj}{Chrome} |
\href{https://addons.mozilla.org/en-US/firefox/addon/codeforces-helper/}{Firefox}
}
\textbf{Codeforces Helper – Browser Extension}
\end{twocolentry}

\begin{highlights}

\item Built a browser extension for Codeforces used by \textbf{2000+ users}.

\item Implemented contest tracking, rating graphs, bookmarking, tag hiding and submission insights.

\item Developed using JavaScript and released on Chrome and Firefox stores.

\end{highlights}

\vspace{0.2cm}

\begin{twocolentry}{
\href{https://github.com/Darelife/MultiEquationSolver}{GitHub}
}
\textbf{Multi-variable Equation Solver}
\end{twocolentry}

\begin{highlights}

\item Developed a C++ solver for linear systems using Gauss–Jordan elimination.

\item Displays intermediate Reduced Row Echelon Form steps for debugging.

\item Detects inconsistent or singular systems using determinant checks.

\end{highlights}

\vspace{0.2cm}

\begin{twocolentry}{
\href{https://aciax.vercel.app}{Website} |
\href{https://github.com/Darelife/aciax}{GitHub}
}
\textbf{ACIAX – Academic Resource Platform}
\end{twocolentry}

\begin{highlights}

\item Built a Next.js platform to organize academic resources for BITS Goa.

\item Integrated Firebase authentication and GitHub contribution workflows.

\item Platform receives \textbf{3000+ monthly views}.

\end{highlights}

\vspace{0.2cm}

\begin{twocolentry}{Mar 2025}
\textbf{PacMan – Network Packet Analyzer}
\end{twocolentry}

\begin{highlights}

\item Built a PCAPNG packet analysis tool with a Flask backend.

\item Used Scapy and Pyshark to extract protocol data and network metrics.

\item Visualized latency, jitter, packet loss and payload data using Next.js frontend.

\item Secured \textbf{2nd place among 200+ teams} in a hackathon.

\end{highlights}

\vspace{0.2cm}

\begin{twocolentry}{Jun 2025 -- Jul 2025}
\textbf{XPIA Attack – AI Agent Exploitation Demo}
\end{twocolentry}

\begin{highlights}

\item Demonstrated cross-platform injection attacks on AI agents.

\item Built using CrewAI, Gemini API, Supabase and PostgreSQL.

\item Implemented prompt parsing, HTTP request handling and attack simulation tools.

\end{highlights}

%------------------------------------------------
\section{Achievements}

\begin{highlights}

\item \textbf{Codeforces Expert} – Peak Rating 1635 (Handle: darelife)

\item Solved 680+ problems and participated in 50+ contests.

\end{highlights}

%------------------------------------------------
\section{Leadership \& Activities}

\begin{twocolentry}{Jan 2025 -- Present}
\textbf{AlgoManiaX: CP Club - Sub Coordinator}
\end{twocolentry}

\begin{highlights}

\item Built club tools and leaderboard infrastructure.

\item Developed Discord bots and cloud workflows for competitions.

\item Created Manim videos explaining Codeforces problems.

\end{highlights}

\vspace{0.2cm}

\begin{twocolentry}{Aug 2024 -- May 2025}
\textbf{Peer Mentorship Program – Mentor}
\end{twocolentry}

\begin{highlights}

\item Mentored 6 first-year students in academics and campus life.

\item Helped them access learning resources and navigate college systems.

\end{highlights}

\end{document}
